\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{LinkedIn Job Market Analysis}
\author{Ahmed Ayman Farouk Shahin \\ AI Engineering Student at Alamein International University, 4th Year}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This document provides an overview of the LinkedIn Job Market Analysis project. The project aims to analyze job postings from LinkedIn to provide insights into the job market trends, including the most in-demand job titles, companies, and locations.

\section{Project Structure}
The project is organized as follows:
\begin{itemize}
    \item \textbf{data/}: Contains the cleaned job data files.
    \item \textbf{scripts/}: Contains Python scripts for data analysis and visualization.
    \item \textbf{reports/}: Contains documentation and reports generated from the analysis.
    \item \textbf{assets/}: Contains any additional resources used in the project.
\end{itemize}

\section{Data Analysis}
The analysis is performed using Python, with libraries such as Pandas and Plotly for data manipulation and visualization. The main script, \texttt{app.py}, is a Streamlit application that provides an interactive dashboard for exploring the job market data.

\section{Interactive Dashboard}
The dashboard includes the following features:
\begin{itemize}
    \item KPI cards showing total job postings, unique companies, and unique locations.
    \item Bar charts for top job titles and companies.
    \item A pie chart for work type distribution.
    \item A line chart for daily job posting trends.
    \item Interactive filters for locations, companies, and work types.
    \item A detailed data table for job postings.
\end{itemize}

\section{Conclusion}
The LinkedIn Job Market Analysis project provides valuable insights into the job market, helping users understand trends and make informed decisions. The interactive dashboard makes it easy to explore the data and gain insights.

\end{document} 